Assessing the Population-level Conservation Effects of Marine Protected Areas

### 2020-07-18 documents/pop-effects-of-mpas-front-matter.Rmd
version submitted to conservation biology

---
title: Assessing the Population-level Conservation Effects of Marine Protected Areas
subtitle: Cover Page
date: "`r Sys.Date()`"
output:
  bookdown::word_document2:
    template: uw.docx
  pdf_document: default
---

Submit your cover page as a separate document. It should NOT be part of the manuscript itself. The cover page must include the title of the paper; an article impact statement (see below); a running head (short title of 20 or fewer characters); a list of 5-8 keywords (do not repeat words in the title); word count (all text from the first word of the Abstract through the last word of the Literature Cited but not including table or figure legends or the body of tables); authors' complete mailing addresses (including street addresses and postal codes) at the time the work was conducted and present addresses if different; name and complete address (including email) of the person to whom correspondence should be sent; and text of your Acknowledgments section.

@@

## Keywords:
  - Marine Protected Area Networks
  - Marine Conservation
  - Program Evaluation
  - Causal Inference
  - Bio-economic Modeling

@@

7166

@@

J

@@

@@

Funding for the simulation model was provided by the NMFS-Sea Grant Population and Ecosystem Dynamics Fellowship. Empirical data collection was funded primarily by the David and Lucille Packard Foundation in support of the Partnership for Interdisciplinary Studies of Coastal Oceans (PISCO) with additional funding from the California Ocean Protection Council and California SeaGrant. This study would not be possible without the work provided by PISCO divers over the years, with special thanks to to Kathyrn Davis Koehn and Avrey Parsons-Field. We also thank Cody Szuwalski, Julia Lawson, André Punt, and two anonymous reviewers for helpful comments and technical support.

>>>>

---
title: "Assessing the Population-level Conservation Effects of Marine Protected Areas"
subtitle: Cover Page
date: "`r Sys.Date()`"
output:
  bookdown::word_document2:
    reference_docx: uw.docx
  pdf_document: default
  word_document: default
---

@@

## Keywords:

Marine Protected Area Networks

Marine Conservation

Program Evaluation

Causal Inference

Bio-economic Modeling

@@

6000

@@

Jennifer E. Caselle
UCSB Marine Science Institute Bldg 520 Rm 4002 Fl 4L 
Santa Barbara, CA 93106-6150 USA
caselle@msi.ucsb.edu

Christopher Costello
Bren Hall 4410 
University of California, Santa Barbara
Santa Barbara, CA 93106-6150 USA
costello@bren.ucsb.edu

Olivier Deschenes
2127 North Hall
University of California, Santa Barbara
Santa Barbara, CA 93106-6150 USA
olivier@econ.ucsb.edu

Steven D. Gaines
Bren Hall 2410 
University of California, Santa Barbara
Santa Barbara, CA 93106-6150 USA
gaines@bren.ucsb.edu

Ray Hilborn
FSH 352B
University of Washington
1122 NE Boat Street
Seattle, WA 98195-5020 USA

Owen Liu
Bren Hall 4330 
University of California, Santa Barbara
Santa Barbara, CA 93106-6150 United States
owen.r.liu@gmail.com

@@

Daniel Ovando
Fishery Science Building
University of Washington
1122 NE Boat Street, Seattle, WA 98195-5020 USA
danovan@uw.edu
phone: (805) 284 6864

@@

Funding for the simulation model was provided by the NMFS-Sea Grant Population and Ecosystem Dynamics Fellowship. Empirical data collection was funded primarily by the David and Lucille Packard Foundation in support of the Partnership for Interdisciplinary Studies of Coastal Oceans (PISCO) with additional funding from the California Ocean Protection Council and California SeaGrant. This study would not be possible without the work provided by PISCO divers over the years, with special thanks to to K. Davis Koehn and A. Parsons-Field. We also thank C. Szuwalski, J. Lawson, and A. Punt for helpful comments and technical support.
